Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-12-07 bayesian-analysis/kundinger-submit-blind.tex
blinded version for sbss.

\begin{aug}
\author{\fnms{Brian} \snm{Kundinger}\thanksref{addr1}\ead[label=e1]{brian.kundinger@duke.edu}},
\author{\fnms{Jerome} \snm{Reiter}\thanksref{addr1}\ead[label=e2]{jreiter@duke.edu}}
\and
\author{\fnms{Rebecca C.} \snm{Steorts}\thanksref{addr2}\ead[label=e3]{beka@stat.duke.edu}}

@@

\address[addr1]{Department of Statistical Science,
  Duke University,
  P.O.\ Box 90251,
  Durham, NC 27708, USA
  \printead{e1}, % print email address of "e1"
  \printead*{e2}
}

\address[addr2]{Departments of Statistical Science and Computer Science,
  Duke University,
  P.O.\ Box 90251,
  Durham, NC 27708, USA
  \printead{e3}
}

@@

>>>>

\begin{aug}
\author{\fnms{Anonymous} \snm{Authors}\thanksref{addr1}\ead[label=e1]{}
%\author{\fnms{} \snm{}\thanksref{addr1}\ead[label=e2]{}}
%\and
%\author{\fnms{} \snm{}\thanksref{addr2}\ead[label=e3]{}
}

@@

\address[addr1]{Anonymous Address
  \printead{e1}, % print email address of "e1"
%  \printead*{e2}
}

%\address[addr2]{Departments of Statistical Science and Computer Science,
%  Duke University,
%  P.O.\ Box 90251,
%  Durham, NC 27708, USA
%  \printead{e3}
%}

@@

%\begin{aug}
%\author{\fnms{Brian} \snm{Kundinger}\thanksref{addr1}\ead[label=e1]{brian.kundinger@duke.edu}},
%\author{\fnms{Jerome} \snm{Reiter}\thanksref{addr1}\ead[label=e2]{jreiter@duke.edu}}
%\and
%\author{\fnms{Rebecca C.} \snm{Steorts}\thanksref{addr2}\ead[label=e3]{beka@stat.duke.edu}}
%
%\runauthor{Kundinger et al.}
%
%\address[addr1]{Department of Statistical Science,
%  Duke University,
%  P.O.\ Box 90251,
%  Durham, NC 27708, USA
%  \printead{e1}, % print email address of "e1"
%  \printead*{e2}
%}
%
%\address[addr2]{Departments of Statistical Science and Computer Science,
%  Duke University,
%  P.O.\ Box 90251,
%  Durham, NC 27708, USA
%  \printead{e3}
%}
%
%%\thankstext{<id>}{<text>}
%\end{aug}
